% Rover Resume - Base Template
% Link: https://github.com/subidit/rover-resume

\documentclass[11pt]{article} % fontsize 10pt/11pt/12pt

\usepackage[margin=1in, a4paper]{geometry}
\setcounter{secnumdepth}{0} % remove section numbering
\usepackage{titlesec}
\titlespacing{\subsection}{0pt}{*0}{*0} % remove vertical spacing above and below
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\large\itshape}
\usepackage{enumitem}
\setlist[itemize]{noitemsep,left=0pt .. \parindent}
\pagestyle{empty} % remove page number
\pdfgentounicode=1


\begin{document}

\begin{center}
	\begin{minipage}{0.5\textwidth}
		{\Huge\bfseries
			Gustavo Lazzari % Name Here
		} \\ \medskip
	\end{minipage} \hfill
	\begin{minipage}{0.4\textwidth}
		\raggedleft
		Email: gustavotlazzari@gmail.com \\
		Mobile: +55 041 987732772 \\
		LinkedIn: linkedin.com/in/glazzari \\
		GitHub: github.com/GLazzari1428 \\
		Curitiba, PR, Brazil
	\end{minipage}
\end{center}

\section{Education}
%=================%
\subsection{Pontifical Catholic University of Paraná $|$ {\normalfont\itshape Computer Science} \hfill 2024-2028}
\begin{itemize}
	\item Expected graduation date: June 2028
	\item Data Structures, Operating Systems, Databases, Object-Oriented Programming
\end{itemize}
\subsection{Swiss School of Curitiba $|$ {\normalfont\itshape High School} \hfill 2017-2020}
\begin{itemize}
	\item Brazilian High School Diploma
	\item IB Bilingual Diploma (International Baccalaureate) $|$ SCORE: 28/45
\end{itemize}

\section{Experience}
%=================%
\subsection{Court of Justice of Paraná \hfill Curitiba, Paraná}
\subsubsection{Software Development Intern \hfill  Aug 2021 - Dec 2022}
\begin{itemize}
    \item Actively participated in the development and maintenance of an academic management system, using various technologies (PHP, MySQL, HTML/CSS).
	\item Implemented and utilized Docker, Docker Compose, and GitHub Actions, streamlining development and deployment processes through CI/CD practices.
	\item Collaborated with team members on feature design, code reviews, debugging, and technical problem-solving, ensuring software quality.
	\item Deployed infrastructure for data hosting and processing on cloud platforms (AWS EC2, GCP Compute Engine).
\end{itemize}


\section{Certifications}
%===============================%
\begin{enumerate}[label=\null, left=0pt..0pt, itemsep=0pt]
    \item Cambridge Advanced English (CAE $|$ Level B2).
	\item Deutsches Sprachdiplom (DSD $|$ Level B1/B2).
%	\item IB Language Diploma (German and English). % Translated commented line
\end{enumerate}

\section{Skills \& Interests}
%===========================%
\begin{description}[itemsep=0pt]
	\item[Technologies] Python, Bash, PHP, JavaScript, C, Java, SQL, Docker, Kubernetes
	\item[Languages] Portuguese (Native), English (Fluent), German (Intermediate).
	\item[Platforms/Hosting] AWS, GCP, Azure, Proxmox, Grafana, Prometheus % "Hospedagem" translated to Platforms/Hosting, "Promox" corrected to "Proxmox"
	\item[Interests] Infrastructure, Music, Hosting, IoT, Home Automation, Linux.
\end{description}

\section{Projects}
%=================
\subsection{Homelab (Home Computing Lab)$|$ \normalfont\textit{self-learning server} \hfill Ongoing} % "em andamento" to "Ongoing"
\begin{itemize}
  \item Utilized Proxmox, Docker, Home Assistant, Virtualization, pfSense, Nginx, Grafana, Kubernetes, Portainer.
  \item Implementation of various industry technologies for the purpose of learning problem-solving.
  \item Learned to use virtualization and automation to implement more robust systems.
\end{itemize}

\end{document}
