% Gustavo Lazzari — Junior Systems Administrator / Infrastructure Engineer
% Generated: 2026-02-26
% Template: Based on Rover Resume (https://github.com/subidit/rover-resume)

\documentclass[10pt]{article}

\usepackage[margin=0.6in, a4paper]{geometry}
\setcounter{secnumdepth}{0}
\usepackage{titlesec}
\titlespacing{\section}{0pt}{5pt}{2pt}
\titlespacing{\subsection}{0pt}{3pt}{1pt}
\titlespacing{\subsubsection}{0pt}{2pt}{1pt}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\normalsize\itshape}
\usepackage{enumitem}
\setlist[itemize]{noitemsep,topsep=1pt,left=0pt .. \parindent}
\setlist[description]{noitemsep,topsep=1pt,itemsep=1pt}
\pagestyle{empty}
\pdfgentounicode=1
\setlength{\parskip}{1pt}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\hypersetup{hidelinks}
\urlstyle{same}

\begin{document}

\begin{center}
	{\LARGE\bfseries Gustavo Lazzari} \\
	\vspace{2pt}
	\href{mailto:gustavotlazzari@gmail.com}{gustavotlazzari@gmail.com} $|$
	+55 41 98773-2772 $|$
	\href{https://www.linkedin.com/in/glazzari}{linkedin.com/in/glazzari} $|$
	\href{https://github.com/GLazzari1428}{github.com/GLazzari1428} $|$
	Curitiba, PR, Brazil
\end{center}

\section{Education}
\subsection{Pontifical Catholic University of Paran\'{a} $|$ {\normalfont\itshape B.Sc. Computer Science} \hfill 2024 -- 2028}
\begin{itemize}
	\item Expected graduation: June 2028 $|$ Operating Systems, Databases, Network Security, Data Structures
\end{itemize}
\subsection{Swiss School of Curitiba $|$ {\normalfont\itshape High School \& IB Bilingual Diploma} \hfill 2017 -- 2020}

\section{Experience}
\subsection{Court of Justice of Paran\'{a} (TJPR) \hfill Curitiba, Brazil}
\subsubsection{IT Infrastructure Intern \hfill Aug 2021 -- Dec 2022}
\begin{itemize}
	\item Provisioned and managed application infrastructure on AWS EC2 and GCP Compute Engine, handling deployment, configuration, and maintenance of production services.
	\item Implemented containerized deployment environments using Docker and Docker Compose, standardizing development and production workflows.
	\item Configured Nginx and Apache web servers for application hosting; automated build and deployment pipelines with GitHub Actions.
\end{itemize}

\section{Projects}
\subsection{Multi-Node Server Cluster $|$ \normalfont\textit{Enterprise-Grade Homelab Infrastructure} \hfill Ongoing}
\begin{itemize}
	\item Architected and operate a two-node Proxmox VE cluster: primary node (Supermicro Xeon E5-2450L, 64GB RAM, Quadro P400) and secondary node (Intel i5, 16GB RAM) hosting 20+ simultaneous VMs and LXC containers.
	\item Manage ZFS storage pools with hands-on experience in disk failure diagnosis, pool recovery, and data integrity monitoring across aging enterprise drives.
	\item Engineered automated backup strategy: secondary node orchestrates all VM/container backups with offsite replication to Google Drive for disaster recovery readiness.
	\item Deployed high-availability DNS infrastructure (PiHole) across both nodes; UPS-protected systems ensuring service continuity during power events.
	\item Configured PCI passthrough (Jellyfin VM) and LXC device mapping (Tdarr) for GPU-accelerated H.265 transcoding via Quadro P400.
\end{itemize}

\subsection{Network Architecture \& Security $|$ \normalfont\textit{Firewall, VPN, Zero Trust} \hfill Ongoing}
\begin{itemize}
	\item Configured VLAN segmentation (IoT/production) with enterprise-grade firewall rules via OPNsense (migrating to OpenWRT); practical knowledge of routing, subnets, and inter-VLAN policies.
	\item Deployed Nginx reverse proxy behind WireGuard VPN for secure internal access; Cloudflare tunnels with Zero Trust and TOTP for public-facing services.
	\item Implemented automated SSL/TLS certificate management via Certbot with Cloudflare DNS challenges for all exposed services.
	\item Self-host identity and credential management: Vaultwarden (password vault) and PocketID (identity provider).
\end{itemize}

\section{Technical Skills}
\begin{description}
	\item[Systems Administration] Linux (Arch/Debian), Proxmox VE (multi-node), Docker, Docker Compose, LXC, systemd, ZFS, RAID
	\item[Networking \& Security] OPNsense, OpenWRT, Nginx, WireGuard, Cloudflare (Tunnels/Zero Trust), PiHole, SSL/TLS, VLANs
	\item[Storage \& Backup] ZFS pool management, disk failure recovery, Proxmox Backup, offsite replication, S.M.A.R.T. monitoring (Scrutiny)
	\item[Monitoring] Prometheus, Grafana, Scrutiny (S.M.A.R.T.)
	\item[Cloud \& Automation] AWS (EC2), GCP, GitHub Actions, Bash, Python, YAML/IaC
	\item[Languages] Portuguese (Native), English (Fluent), German (Intermediate)
\end{description}

\section{Certifications}
Cambridge Advanced English (CAE -- B2) $|$ Deutsches Sprachdiplom (DSD -- B1/B2) $|$ Currently pursuing: AWS Certified Cloud Practitioner (CLF-C02)

\end{document}
