% Gustavo Lazzari — IoT & Home Automation Engineer
% Generated: 2026-02-26
% Template: Based on Rover Resume (https://github.com/subidit/rover-resume)

\documentclass[10pt]{article}

\usepackage[margin=0.6in, a4paper]{geometry}
\setcounter{secnumdepth}{0}
\usepackage{titlesec}
\titlespacing{\section}{0pt}{5pt}{2pt}
\titlespacing{\subsection}{0pt}{3pt}{1pt}
\titlespacing{\subsubsection}{0pt}{2pt}{1pt}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\normalsize\itshape}
\usepackage{enumitem}
\setlist[itemize]{noitemsep,topsep=1pt,left=0pt .. \parindent}
\setlist[description]{noitemsep,topsep=1pt,itemsep=1pt}
\pagestyle{empty}
\pdfgentounicode=1
\setlength{\parskip}{1pt}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\hypersetup{hidelinks}
\urlstyle{same}

\begin{document}

\begin{center}
	{\LARGE\bfseries Gustavo Lazzari} \\
	\vspace{2pt}
	\href{mailto:gustavotlazzari@gmail.com}{gustavotlazzari@gmail.com} $|$
	+55 41 98773-2772 $|$
	\href{https://www.linkedin.com/in/glazzari}{linkedin.com/in/glazzari} $|$
	\href{https://github.com/GLazzari1428}{github.com/GLazzari1428} $|$
	Curitiba, PR, Brazil
\end{center}

\section{Education}
\subsection{Pontifical Catholic University of Paran\'{a} $|$ {\normalfont\itshape B.Sc. Computer Science} \hfill 2024 -- 2028}
\begin{itemize}
	\item Expected graduation: June 2028 $|$ Operating Systems, Databases, Network Security, Data Structures
\end{itemize}
\subsection{Swiss School of Curitiba $|$ {\normalfont\itshape High School \& IB Bilingual Diploma} \hfill 2017 -- 2020}

\section{Experience}
\subsection{Court of Justice of Paran\'{a} (TJPR) \hfill Curitiba, Brazil}
\subsubsection{IT Intern \hfill Aug 2021 -- Dec 2022}
\begin{itemize}
	\item Deployed and maintained containerized applications using Docker and Docker Compose on cloud infrastructure (AWS EC2, GCP Compute Engine).
	\item Implemented CI/CD automation with GitHub Actions; configured Nginx and Apache web servers for application hosting.
\end{itemize}

\section{Projects}
\subsection{Smart Home IoT Network $|$ \normalfont\textit{10+ ESP32 Devices / ESPHome / MQTT} \hfill Ongoing}
\begin{itemize}
	\item Deploy and maintain a network of 10+ ESP32 microcontrollers for smart lighting control, intelligent switches, and ambient LED installations (WLED), fully configured via ESPHome using YAML and Jinja2 templating.
	\item Integrate all IoT devices with Home Assistant through MQTT for centralized automation rules, scheduling, and real-time monitoring of the home environment.
	\item Currently building a custom Home Assistant remote controller using salvaged Cherry MX mechanical switches and an ESP32, designed and configured entirely through ESPHome.
	\item Replaced commercial voice assistants (Alexa) with custom ESP32-based solutions, maintaining full local control without cloud dependencies.
\end{itemize}

\subsection{AI-Powered Security \& Surveillance $|$ \normalfont\textit{Frigate NVR / Object Detection} \hfill Ongoing}
\begin{itemize}
	\item Deployed Frigate NVR for real-time local video processing with AI-driven object detection, integrated with Home Assistant for automated alerting and event-driven actions.
	\item Configured GPU-accelerated video processing pipeline using Quadro P400 with hardware passthrough in Proxmox VE.
\end{itemize}

\subsection{Supporting Server Infrastructure $|$ \normalfont\textit{Proxmox / Docker / Monitoring} \hfill Ongoing}
\begin{itemize}
	\item Operate a two-node Proxmox VE cluster (20+ VMs/LXCs) providing the backbone for all IoT services, including MQTT brokers, Home Assistant, Frigate, and monitoring infrastructure.
	\item Configured secure remote access via WireGuard VPN and Cloudflare Zero Trust, enabling reliable control of home automation from anywhere.
	\item Maintain observability with Prometheus and Grafana for system metrics, Scrutiny for disk health monitoring, and automated backups with offsite replication.
\end{itemize}

\section{Technical Skills}
\begin{description}
	\item[IoT \& Embedded] ESP32, ESPHome (YAML/Jinja2), MQTT, WLED, sensor integration, relay control, microcontroller deployment
	\item[Home Automation] Home Assistant (advanced automations, integrations), Frigate NVR (AI object detection), Navidrome
	\item[Hardware \& Electronics] Soldering (8+ years daily experience), component-level repair, desoldering, PCB modification, custom enclosure design
	\item[Infrastructure] Linux Admin (Arch/Debian), Proxmox VE, Docker, Docker Compose, ZFS, systemd
	\item[Networking] WireGuard, Cloudflare (Tunnels/Zero Trust), Nginx, PiHole, OPNsense, VLAN segmentation
	\item[Scripting \& Automation] Bash, Python, YAML/IaC, GitHub Actions
	\item[Languages] Portuguese (Native), English (Fluent), German (Intermediate)
\end{description}

\section{Certifications}
Cambridge Advanced English (CAE -- B2) $|$ Deutsches Sprachdiplom (DSD -- B1/B2) $|$ Currently pursuing: AWS Certified Cloud Practitioner (CLF-C02)

\end{document}
