% Gustavo Lazzari -- AI Internship CV (EN)
% Updated: 2026-05-25
% Framing: AI Infrastructure / Applied AI (honest -- no ML training experience)

\documentclass[10.5pt]{article}

\usepackage[margin=0.6in, a4paper]{geometry}
\setcounter{secnumdepth}{0}
\usepackage{titlesec}
\titlespacing{\section}{0pt}{5pt}{2pt}
\titlespacing{\subsection}{0pt}{3pt}{1pt}
\titlespacing{\subsubsection}{0pt}{2pt}{1pt}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\normalsize\itshape}
\usepackage{enumitem}
\setlist[itemize]{noitemsep,topsep=1pt,left=0pt .. \parindent}
\setlist[description]{noitemsep,topsep=1pt,itemsep=1pt}
\pagestyle{empty}
\pdfgentounicode=1
\setlength{\parskip}{1pt}
\linespread{1.15}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\hypersetup{hidelinks}
\urlstyle{same}

\begin{document}

\begin{center}
    {\LARGE\bfseries Gustavo Lazzari} \\
    \vspace{2pt}
    \href{mailto:gustavotlazzari@gmail.com}{gustavotlazzari@gmail.com} $|$
    +55 41 98773-2772 $|$
    \href{https://www.linkedin.com/in/glazzari}{linkedin.com/in/glazzari} $|$
    \href{https://github.com/GLazzari1428}{github.com/GLazzari1428} $|$
    Curitiba, PR, Brazil
\end{center}

\section{Profile}
Computer Science student with hands-on experience deploying AI inference workloads on self-managed
infrastructure. Runs Frigate NVR with real-time object detection in a production homelab backed by
Linux, Docker, and a GPU-capable Proxmox cluster. Strong infrastructure foundation relevant to
AI deployment and MLOps roles. Fluent English (CAE C1), German B2 (DSD II).
EU eligibility from Jan 2027 (Italian citizenship).

\section{Education}
\subsection{Pontifical Catholic University of Paran\'{a} $|$ {\normalfont\itshape B.Sc. Computer Science} \hfill 2024 -- 2028}
\begin{itemize}
    \item Expected graduation: March 2028. Coursework: Data Structures, Algorithms, Operating Systems, Databases.
\end{itemize}
\subsection{Swiss School of Curitiba $|$ {\normalfont\itshape IB Bilingual Diploma} \hfill 2017 -- 2020}

\section{Experience}
\subsection{Court of Justice of Paran\'{a} (TJPR) \hfill Curitiba, Brazil}
\subsubsection{IT Intern \hfill Aug 2021 -- Dec 2022}
\begin{itemize}
    \item Built a PHP web application (backend and frontend) for certificate management and
          administrative workflows of the TJPR School of Magistracy.
    \item Containerized the application with Docker and Docker Compose; deployed on AWS EC2;
          automated deployments with GitHub Actions; MySQL as the relational database.
    \item Configured Nginx as web server and reverse proxy.
\end{itemize}

\section{Projects}
\subsection{AI Inference on Homelab Infrastructure $|$ \normalfont\textit{Frigate NVR / Proxmox} \hfill Ongoing}
\begin{itemize}
    \item Runs Frigate NVR with real-time object detection (AI inference) on a self-managed, GPU-capable
          Proxmox VE cluster; integrates detection events with Home Assistant for automated responses.
    \item Containerized inference workloads run on a hardened Linux environment with VLAN-segmented
          networking, WireGuard VPN, and Cloudflare Zero Trust access control.
    \item Experimented with local LLM deployment (Ollama) on homelab hardware; familiar with
          quantized model inference on consumer-grade GPUs.
\end{itemize}
\subsection{Homelab -- Infrastructure for AI Workloads $|$ \normalfont\textit{Proxmox / Docker / Linux} \hfill Ongoing}
\begin{itemize}
    \item Two-node Proxmox VE cluster with GPU passthrough, ZFS storage, and full observability
          via Prometheus and Grafana -- capable of serving containerized AI/ML workloads.
    \item Automated backup pipeline with offsite replication and monitoring via Scrutiny (S.M.A.R.T.).
\end{itemize}

\section{Technical Skills}
\begin{description}
    \item[Applied AI] Frigate NVR (object detection inference), local LLM deployment (Ollama), Home Assistant AI integration
    \item[Infrastructure] Linux Admin, Proxmox VE (GPU passthrough), Docker/Compose, LXC, ZFS
    \item[Networking] OPNsense, WireGuard, VLANs, Cloudflare ZT/Tunnels, Nginx, DNS/DHCP
    \item[Monitoring] Prometheus, Grafana, Scrutiny (S.M.A.R.T.)
    \item[Programming] Python (basic scripts), PHP, Bash, Git, GitHub Actions
    \item[Languages] Portuguese (Native), English (Fluent -- CAE C1), German (B2 -- DSD II), Italian (Basic)
\end{description}

\section{Certifications}
Cambridge Advanced English -- CAE C1 $|$ Deutsches Sprachdiplom -- DSD II B2 $|$ In progress: CCNA 200-301

\end{document}
